Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 egpaper_final.tex

We empirically found out that NZ-WHO performs reasonably well without time consuming calibration stage compare to other variational methods to generate templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4 elevations with 250 cells per each template. Each template takes approximately 70 milliseconds to generate a NZ-WHO template. We also calibrated templates using the method presented in \cite{Aubry14}. Briefly, the calibration learns affine transformation of the detection confidence using a set of natural images.% Note that in Section \ref{experiments}, we provide the same experiment with 9 CAD models.

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calibration  & time & after Calibration \cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0  &  31ms  & 60.4 / 50.2                 &   8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4  &  3811ms&                             &   12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms &     83.7 / 87.3             &   8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1  &  103ms & \textbf{92.8} / 86.7 &   8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG        & \textbf{90.0} / 82.8 & 79ms & 90.3 / \textbf{86.8}                   &  8.5 sec   \\
\hline
\end{tabular}
\\\textcolor{red}{TABLE REQUIRES MODIFICATION}
\end{center}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table*}

@@

In this section, we validate our proposed NZ-WHO templates in two different ways. First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints. Then we run the bank of NZ-WHO templates as an ensemble of weak classifiers and show that our method can work as a standalone detector for simple task. This validates that our ensemble of NZ-WHO templates, though each of templates takes 70ms to generate from a rendering image, can robustly perform 2D-3D matching on real images.

@@

We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}. MPPE is the average of viewpoint accuracy.

Our ensemble of NZ-WHO templates is generated from rendering image with no calibration but shows strong performance on object detection. The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}. Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.

>>>>

We empirically found out that NZ-WHO performs reasonably well without time consuming calibration stage compare to other variational method to generate templates. We used 1 CAD model with viewpoints covering 24 azimuths and 4 elevations. Each template takes approximately 80 milliseconds to generate a NZ-WHO template. We also calibrated templates using the method presented in \cite{Aubry14}. The calibration learns affine transformation of the detection confidence.% Note that in Section \ref{experiments}, we provide the same experiment with 9 CAD models.

\begin{table*}[!htbp]
    \begin{center}
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calibration  & time & after Calibration \cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0  &  31ms  & 60.4 / 50.2                 &   8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4  &  3811ms&                             &   12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms &     83.7 / 87.3             &   8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1  &  103ms & \textbf{92.8} / 86.7 &   8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG        & \textbf{90.0} / 82.8 & 79ms & 90.3 / \textbf{86.8}                   &  8.5 sec   \\
\hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table*}

@@

In this section, we validate our proposed NZ-WHO templates in two different ways. First, we make a set of NZ-WHO templates for a set of CAD models from various viewpoints. Then we run the bank of NZ-WHO templates as ensembles of weak detectors and show that the rendering image can be We want to see how robust the NZ-WHO to real images a

@@

We created ensemble of NZ-WHO templates using 9 CAD models and measured the Average Precision (AP) of object detection task and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11}. MPPE is the average of viewpoint accuracy.  
\subsection{Object Detection} 
Instance-level 2D-3D matching (registration) is a difficult problem since we need a CAD model that looks similar to the object in the image. Especially, due to extreme intraclass variability of chair \cite{Aubry14} used a very large collection of CAD models to cover variety of chairs. Similarly, \cite{Lim14}
Our ensemble of NZ-WHO templates is generated from rendering image with no calibration but shows strong performance on object detection. The baseline method are Aspect Layout Model (ALM) \cite{Xiang12} and VOC-DPM \cite{Pepik12}. Note that the baseline methods require complex 3D modeling and viewpoint annotated natural images.

### 2014-11-14 intro.tex

\begin{figure}[t]
  \centering
  % \includegraphics[width=0.9\linewidth]{schematics} 
  \includegraphics[width=0.99\linewidth]{front} % \\[-5pt]
  % (a)\\[0pt]
  % \setlength\tabcolsep{0pt}
  % \begin{tabular}{cc}
  %     \includegraphics[width=0.45\linewidth]{car/orig2} & 
  %     \includegraphics[width=0.45\linewidth]{car/overlay2}
  %  %   \begin{tabular}{cc}
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2001-2004 Ford Ranger Edge} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2002 Dodge Ram FedEx} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2007-Nissan-Versa-_-Tiida-SL} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2008-Jeep-Cherokee} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2009 Toyota Cargo} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2010-Chevrolet-Aveo5-LT} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2012-Citroen-DS4}  
  %  %   \end{tabular}
  % \end{tabular}\\
  % (b)
  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detecting objects directly or initializing pose of an object in the bounding box from other detectors. Once the initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
  % \vspace{-1em}
  \label{fig:front}
\end{figure}

>>>>

\begin{figure}[t]
  \centering
  % \includegraphics[width=0.9\linewidth]{schematics} 
  \includegraphics[width=0.99\linewidth]{front} % \\[-5pt]
  % (a)\\[0pt]
  % \setlength\tabcolsep{0pt}
  % \begin{tabular}{cc}
  %     \includegraphics[width=0.45\linewidth]{car/orig2} & 
  %     \includegraphics[width=0.45\linewidth]{car/overlay2}
  %  %   \begin{tabular}{cc}
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2001-2004 Ford Ranger Edge} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2002 Dodge Ram FedEx} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2007-Nissan-Versa-_-Tiida-SL} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2008-Jeep-Cherokee} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2009 Toyota Cargo} & 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2010-Chevrolet-Aveo5-LT} \\ 
  %  %       \includegraphics[width=0.16\linewidth]{cad_car/2012-Citroen-DS4}  
  %  %   \end{tabular}
  % \end{tabular}\\
  % (b)
  \caption{Using a bank of CAD models, we generate NZ-WHO templates which can be used to either detect objects directly or initialize pose of an object in the bounding box from other detectors. Once initialization is given, we use NZ-WHO to propose and validate plausible pose on-the-fly and further tune the translation, 3D viewpoint and focal length continuously.}
  % \vspace{-1em}
  \label{fig:front}
\end{figure}
